Compensated de Casteljau algorithm in \(K\) times the working precision

### 2018-05-16 doc/paper.tex
Making image symlinks in doc directory.
Referring to these images in `paper.tex`. This will
make it easier on the journal to build the source.

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{../images/horner_inferior.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Comparing Horner's method to the de Casteljau method for
    evaluating \(p(s) = (2s - 1)^3\) in the neighborhood of its
    multiple root \(1/2\).}
  \label{fig:horner-inferior}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.8125\textwidth]{../images/jlcs10_plot.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    represented in Bernstein form.}
  \label{fig:jlcs-10}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{../images/compensated_insufficient.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{The compensated de Casteljau method starts to lose accuracy
    for \(p(s) = (2s - 1)^3 (s - 1)\) in the neighborhood of its
    multiple root \(1/2\).}
  \label{fig:compensated-insufficient}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{../images/de_casteljau_smooth_drawing.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    in the neighborhood of its multiple root \(3/4\).}
  \label{fig:smooth-drawing}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.8125\textwidth]{../images/de_casteljau_rel_error.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Accuracy of evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    represented in Bernstein form.}
  \label{fig:compensated-k}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{horner_inferior.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Comparing Horner's method to the de Casteljau method for
    evaluating \(p(s) = (2s - 1)^3\) in the neighborhood of its
    multiple root \(1/2\).}
  \label{fig:horner-inferior}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.8125\textwidth]{jlcs10_plot.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    represented in Bernstein form.}
  \label{fig:jlcs-10}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{compensated_insufficient.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{The compensated de Casteljau method starts to lose accuracy
    for \(p(s) = (2s - 1)^3 (s - 1)\) in the neighborhood of its
    multiple root \(1/2\).}
  \label{fig:compensated-insufficient}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{de_casteljau_smooth_drawing.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    in the neighborhood of its multiple root \(3/4\).}
  \label{fig:smooth-drawing}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.8125\textwidth]{de_casteljau_rel_error.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Accuracy of evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    represented in Bernstein form.}
  \label{fig:compensated-k}
\end{figure}
